Latitudinal gradients in biotic niche breadth vary across ecosystem types.

### 2018-04-16 manuscript/latitudepaper.tex
updated nonTS versions. Doesn't look so bad, actually

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}

@@

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=0.891 for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
  lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

>>>>

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{soul}

@@

  Link density (mean number of feeding links per species), generality (mean
  number of prey per species), and vulnerability (mean number of predators per
  species) were strongly and positively correlated ($R^2$=\st{0.891}0.890 for link
  density and generality, $R^2$\textgreater0.999 for link density and
  vulnerability, and $R^2$=\st{0.890}0.889 for generality and vulnerability). Contrary
  to the expected latitudinal gradient, the best-fit version of
  equation~(\ref{Latfull}) did not include a significant
  effect of latitude on species richness for any ecosystem type. Further, there were no significant
  relationships between link density, generality, or vulnerability with
  latitude for any ecosystem type.
  % [[After correction: $R^2$=0.890 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.889 for generality and vulnerability.]]

  % [[Coefficients are from LS_min, etc. Need to re-run for non_TS and TS webs, update with new minimum models.]]

  Each measure of specialisation increased with increasing
  species richness ($\beta_0$=\st{0.637}0.668, $p$\textless0.001; $\beta_0$=\st{0.553}0.689,
  $p$\textless0.001; and $\beta_0$=\st{0.637}0.668, $p$\textless0.001, respectively;
  Fig.~\ref{props_v_lat}). 
  % [[After correction: ($\beta_0$=0.668, $p$\textless0.001; $\beta_0$=0.689, $p$\textless0.001; and $\beta_0$=0.668, $p$\textless0.001, respectively).]]
  For estuarine, marine, and terrestrial food webs the
  strength of this scaling did not vary with latitude
  (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
  $\beta_{Latitude}$=\st{-0.001}-0.002, $p$=\st{0.535}0.101 for generality; 
  latitude was not retained in the best-fit models for link density or vulnerability \st{and
  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
  % [[After correction: latitude not included in LS_min or Vul_min. $\beta_{Latitude}$=-0.002, $p$=0.101 for generality]]
  \st{In lake food webs, however, the scaling of each property was stronger towards
  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
  webs, generality increased more rapidly towards the poles
  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
  vulnerability did not vary with latitude (i.e., the interaction term 
  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
  In lake and stream food webs, however, the scaling of generality was stronger
  towards the poles. This change in scaling was significant for streams but not for
  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
  % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively). Generality scaled significantly more strongly towards the poles in streams and slightly (not significantly) more strongly towards the poles in lake food webs ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively). ]]

  [[[[[Need to double-check and update this. Then adjust discussion as needed.]]]]]
  [[Note: The trophic species version of the webs changed less with the correction. For link density, $\beta_{Latitude:Lake}$=0.005, $p$=0.002. For generality, $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001 and $\beta_{Latitude:Stream}$=0.004, $p$=0.009. For vulnerability, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.]]
